---
surname: Mark Fransham
position: "Senior Research Officer and Departmental Lecturer in Quantitative Methods"
address: "Dept of Social Policy & Intervention, University of Oxford, 32 Wellington Square, Oxford OX1 2ER"
phone: +44 (0)1865 270352
www: mfransham.github.io
email: mark.fransham@spi.ox.ac.uk
headcolor: "414141"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Current positions

```{r}
tribble(
  ~position, ~institution, ~date, 
  "Senior Research Officer", "Department of Social Policy & Intervention, University of Oxford", "Jan 2021 - ",
  "Departmental Lecturer in Quantitative Methods", "Department of Social Policy & Intervention, University of Oxford", "Sep 2020 - ", 
"Junior Research Fellow", "Wolfson College, University of Oxford", "Oct 2020 - ", 
"Visiting Fellow", "International Inequalities Institute, London School of Economics & Political Science", "Oct 2020 - "
) %>% 
  detailed_entries(what = institution, with = position, when = date)
```

# Previous positions

```{r}
tribble(
  ~position, ~institution, ~date, 
  "Research Officer", "International Inequalities Institute, London School of Economics & Political Science", "2018-2020", 
  "Social Statistics Officer", "Oxford City Council", "2007-2016", 
  "Policy Officer (Social Inclusion & Health Inequalities)", "Oxford City Council", "2005-2007", 
  "Cancer Information Analyst", "Cancer Information Analyst", "2004-2005", 
  "Research & Evaluation Officer", "Nacro", "2002-2004"
) %>% 
  detailed_entries(what = institution, with = position, when = date)
```

# Education

```{r}
tribble(
  ~qual, ~institution, ~date, ~details,
  "DPhil in Geography & the Environment", "School of Geography & the Environment, University of Oxford", "2015-2018", c("Thesis title: *Understanding neighbourhood income poverty dynamics in England*", 
  "Supervisors Professor Danny Dorling and Dr Rachel Loopstra",
  "Passed without corrections"),
  "MSc Applied Social Studies / Diploma in Social Work", "Department of Social Policy and Social Work, University of Oxford", "2000-2002", character(),
  "BA Hons Physics 2:1", "St Catherine’s College, University of Oxford", "1995-1998", character()) %>% 
  detailed_entries(what = institution, with = qual, when = date, why = details)
```

# Publications

## Works in progress

Fransham, M., Herbertson, M., Pop, M., Bandeira Morais, M., Lee, N. (in preparation) Level best? The levelling up agenda and UK regional inequality.

Fransham, M., Bauluz, L., Breau, S., Lee, N. & Verdugo, G., (in preparation) International trends in geographic income inequality: a method for assessing the comparability of spatial units.  

## Peer-reviewed journal articles

Reeves, A., Fransham, M., Stewart, K., & Patrick, R. (2021). Does capping social security harm health? A natural experiment in the UK. *Social Policy & Administration*. https://doi.org/10.1111/spol.12768 ([Guardian](https://www.theguardian.com/commentisfree/2021/oct/03/universal-credit-cut-will-risk-the-health-of-millions) | [New Psychotherapist](https://www.psychotherapy.org.uk/media/otzimjco/79-new-psychotherapist-winter-spring-2022.pdf))

Koch, I., Fransham, M., Cant, S., Ebrey, J., Glucksberg, L., & Savage, M. (2020). Social Polarisation at the Local Level: A Four-Town Comparative Study on the Challenges of Politicising Inequality in Britain, *Sociology*, 55(1), 3–29. https://doi.org/10.1177/0038038520975593 (nominated for [2022 SAGE Prize for Innovation/Excellence](https://www.britsoc.co.uk/opportunities/sage-prize-for-innovationexcellence/))

Fransham, M. (2020) Neighbourhood gentrification, displacement, and poverty dynamics in post-recession England, *Population, Space and Place*, 25(5):e2327.  https://doi.org/10.1002/psp.2327 

Fransham, M. (2019) Increasing evenness in the neighbourhood distribution of income poverty in England 2005–2014: Age differences and the influence of private rented housing, *Environment and Planning A: Economy and Space* 51(2), 403–419. https://doi.org/10.1177/0308518X18792569 

Fransham, M. (2019) Income and Population Dynamics in Deprived Neighbourhoods: Measuring the Poverty Turnover Rate Using Administrative Data, *Applied Spatial Analysis and Policy* 12(2), 275-300. https://link.springer.com/article/10.1007/s12061-017-9242-6 

## Working papers and other publications

Fransham, M. (forthcoming). Poverty. In D. Demeritt & L. Lees (Eds.), *Concise Encyclopedia of Human Geography*. Edward Elgar.

Reeves, A., Fransham, M., Stewart, K., & Patrick, R. (2021). *Does capping social security harm health? A natural experiment in the UK*. Working Paper CASE/221, Centre for Analysis of Social Exclusion, London School of Economics & Political Science. https://sticerd.lse.ac.uk/dps/case/cp/casepaper221.pdf

Koch, I., Fransham, M., Cant, S., Ebrey, J., Glucksberg, L. and Savage, M. (2019) *Social polarisation at the local level: a four-town comparative study*. Working Paper (37). International Inequalities Institute, London School of Economics & Political Science, London, UK. http://eprints.lse.ac.uk/102216/

Fransham, M., & Dorling, D. (2018). Homelessness and Public Health. *British Medical Journal*, 360, k214. https://doi.org/10.1136/bmj.k214 

Fransham, M., & Dorling, D. (2017). Have mortality improvements stalled in England? *British Medical Journal*, 1946, j1946. http://doi.org/10.1136/bmj.j1946

Fransham, M., & Dorling, D. (2017, April 8). Oxford academics: “House prices can keep rising only if the Government backs mass buy-to-let.” *The Telegraph*. London. (http://www.telegraph.co.uk/investing/buy-to-let/oxford-academics-house-prices-can-keep-rising-government-backs/)

# Funding

ESRC Open Research Area 6 funding for *Linking National and Regional Income Inequality: Cross-Country Data Harmonization and Analysis*. Total ESRC funding £458,480; total project funding approx £1.2 million (grant number ES/V013548/1)

3 year joint ESRC/EPSRC studentship, Social Sciences Doctoral Training Centre, University of
Oxford (grant numbers ES/J500112/1, EP/K503113/1, EP/L505031/1, EP/M50659X/1)

# Teaching experience

## Current teaching at University of Oxford

BA Philosophy, Politics and Economics / History & Politics / Human Sciences

- Social Policy 224 undergraduate option

MSc/MPhil Evidence-Based Social Intervention and Policy Evaluation

- Quantitative Analysis module
- Evaluation Methods module
- Social Policy Analysis module
- Thesis supervision

MSc/MPhil Comparative Social Policy

- Social Policy Analysis module
- Thesis supervision

DPhil (PhD) Social Policy / Social Intervention & Policy Evaluation

- Methods Hub
- Transfer of Status and Confirmation of Status assessments

## Past teaching

- London School of Economics Masterclass *Inequality and Social Cohesion: A Global Perspective* for Fundacion Ramon Areces, Madrid (July 2019)
- MSc Inequalities and Social Science, London School of Economics: dissertation supervision (2018-2020)
- BA Philosophy, Politics and Economics, University of Oxford: Social Policy 224 undergraduate option (2017-2019, as a college tutor)
- BA Geography, University of Oxford: Applied Statistics module (2017, as teaching assistant)

# Administrative and professional service experience

## Advisory positions

Government Statistical Service Migration Statistics Expert Group \hfill 2020-current 		
Member of Council, British Society for Population Studies \hfill 2019-current 		
UK Population Theme Advisory Board, Office for National Statistics \hfill 2016-current 		
Local Authority Co-Chair, Local Government Association CLIP Population Subgroup \hfill 2013-2015	
Official Statistics Committee, Royal Statistical Society \hfill 2012-2014       
Chair, Oxfordshire Data Observatory \hfill 2008-2010	

## Peer review

Reviewer for *Journal of the Royal Statistical Society Series A*, *Social Science & Medicine*, *SSM - Population Health*, *Cambridge Journal of Regions, Economy & Society*, *Regional Studies*, *BMJ Open*, *Journal of Social Policy* and *Urban Studies*.

## Administrative service

Ethics Committee, Department of Social Policy & Intervention, University of Oxford \hfill 2021-current        
Teaching Committees for MSc in Evidence-Based Social Intervention and Policy Evaluation and MSc in Comparative Social Policy, Department of Social Policy & Intervention, University of Oxford \hfill 2020-current        
Research Committee, International Inequalities Institute, London School of Economics  \hfill 2019-2010        
Equality and Diversity Committee, School of Geography & the Environment, University of Oxford (Contributed to the successful application for an Athena SWAN Bronze Award) \hfill 2015-2017         

## Professional membership

Royal Statistical Society (2010-), British Society for Population Studies (2014-), Social Policy Association (2017-) and Regional Studies Association (2018-)
